# Data transformation

## Data Cleaning
The original data is as follows:
```{r,echo=FALSE}
fifa_data=read.csv("/Users/a1119/Desktop/2021/FIFA21.csv")
head(fifa_data)
```

Most of the columns could be directly used. However, there are several columns that we need to clean. The three columns we first want to clean is Weak.Foot, Skill.Moves and International.Reputation. These three columns are rate of the player for these three aspects, rating from 1 star to 5 star. In order to make these columns work in our future visualization, we decide to remove the star sign after the rating, changing the data type from char to int.

Secondly, we want to clean the position statistics for each player from column LS to column GK. The original data format is "int+int" (i.e.87+3). We decided to only keep the number before the plus sign to represent the rating.

Finally, another column we want to clean is Working.Rate. This column represents data in a format i.e. "High/Low". We decide to split this column into two column: working_rate1 and working_rate2 by "/". The working rate before "/" is attack work rate. The working rate after "/" is defense work rate.

After transformation, the data looks like:

```{r,echo=FALSE}
library(strex)
library(magrittr)
library(tibble)
Weak_Foot=str_first_number(fifa_data$Weak.Foot)
fifa_data$Weak.Foot=Weak_Foot

skill_moves=str_first_number(fifa_data$Skill.Moves)
fifa_data$Skill.Moves=skill_moves

international_reputation=str_first_number(fifa_data$International.Reputation)
fifa_data$International.Reputation=international_reputation


LS=str_first_number(fifa_data$LS)
fifa_data$LS=LS

ST=str_first_number(fifa_data$ST)
fifa_data$ST=ST

RS=str_first_number(fifa_data$RS)
fifa_data$RS=RS

LW=str_first_number(fifa_data$LW)
fifa_data$LW=LW

LF=str_first_number(fifa_data$LF)
fifa_data$LF=LF

CF=str_first_number(fifa_data$CF)
fifa_data$CF=CF

RF=str_first_number(fifa_data$RF)
fifa_data$RF=RF

RW=str_first_number(fifa_data$RW)
fifa_data$RW=RW

LAM=str_first_number(fifa_data$LAM)
fifa_data$LAM=LAM

CAM=str_first_number(fifa_data$CAM)
fifa_data$CAM=CAM

RAM=str_first_number(fifa_data$RAM)
fifa_data$RAM=RAM

LM=str_first_number(fifa_data$LM)
fifa_data$LM=LM

LCM=str_first_number(fifa_data$LCM)
fifa_data$LCM=LCM

CM=str_first_number(fifa_data$CM)
fifa_data$CM=CM

RCM=str_first_number(fifa_data$RCM)
fifa_data$RCM=RCM

RM=str_first_number(fifa_data$RM)
fifa_data$RM=RM

LWB=str_first_number(fifa_data$LWB)
fifa_data$LWB=LWB

LDM=str_first_number(fifa_data$LDM)
fifa_data$LDM=LDM

CDM=str_first_number(fifa_data$CDM)
fifa_data$CDM=CDM

RDM=str_first_number(fifa_data$RDM)
fifa_data$RDM=RDM

RWB=str_first_number(fifa_data$RWB)
fifa_data$RWB=RWB

LB=str_first_number(fifa_data$LB)
fifa_data$LB=LB

LCB=str_first_number(fifa_data$LCB)
fifa_data$LCB=LCB

CB=str_first_number(fifa_data$CB)
fifa_data$CB=CB


RCB=str_first_number(fifa_data$RCB)
fifa_data$RCB=RCB

RB=str_first_number(fifa_data$RB)
fifa_data$RB=RB

GK=str_first_number(fifa_data$GK)
fifa_data$GK=GK

work_rate=data.frame(strsplit(fifa_data$Work.Rate,split = "/ "))
work_rate=t(as.matrix(work_rate))

work_rate_attack=work_rate[,1]
work_rate_defense=work_rate[,2]
fifa_data=fifa_data%>% add_column(work_rate_attack,.after=19)
fifa_data=fifa_data%>% add_column(work_rate_defense,.after=20)

head(fifa_data)
```

